Characterizing Stellar Streams by ML

### 2023-08-28 src/tex/ms.tex
[showyourwork] overleaf sync

    We generate synthetic stream observations by sampling uniformly in $\phi_1$
    In $\phi_2$ we sample from a quadratic in $\phi_1$ with normally-distributed
    $0.15\degree$ scatter.  The distances are sampled from a linear funciton in
    $\phi_1$ with normally-distributed $0.25 \unit{kpc}$ scatter, then
    transformed to the parallax $\parallax$.  Non-poissonian density variations
    are then simulated by evaluating the stream density with two Gaussian
    distributions centered at different values of $\phi_1$ with random
    amplitudes (which sum to $1$) and widths.  Stream stars are then removed
    using random sampling, weighted by their likelihood of belonging to the
    density. The background astrometric points in are generated from exponential
    distributions at each $\phi_1$.  The number of stream stars is
    $\variable{output/mock/nstream_variable.txt}$, while the number of
    background stars is $\variable{output/mock/nbackground_variable.txt}$.

@@

    We pre-train a normalizing flow (see
    \autoref{sub:method:photometric_model:off_stream}) on an off-stream
    selection.  We train on the photometry.  You can see the selection in
    \auroref{fig:mock_data_photometric_background_selection}.  You can see both
    the on-stream and off-stream labels, blue and black respectively.  We select
    using an astrometric selection. In the photometry you can see that the
    on-stream selection has two populations, drawn from the isochrone and drawn
    from the background The off-stream selection, meanwhile, has only the
    background population. Next we train the full model.

>>>>

    We generate synthetic stream observations by sampling uniformly in $\phi_1$
    In $\phi_2$ we sample from a quadratic in $\phi_1$ with normally-distributed
    $0.15^{\circ}$ scatter.  The distances are sampled from a linear funciton in
    $\phi_1$ with normally-distributed $0.25 \unit{kpc}$ scatter, then
    transformed to the parallax $\parallax$.  Non-poissonian density variations
    are then simulated by evaluating the stream density with two Gaussian
    distributions centered at different values of $\phi_1$ with random
    amplitudes (which sum to $1$) and widths.  Stream stars are then removed
    using random sampling, weighted by their likelihood of belonging to the
    density. The background astrometric points in are generated from exponential
    distributions at each $\phi_1$.  The number of stream stars is
    $\variable{output/mock/nstream_variable.txt}$, while the number of
    background stars is $\variable{output/mock/nbackground_variable.txt}$.

@@

    We pre-train a normalizing flow (see
    \autoref{sub:method:photometric_model:off_stream}) on an off-stream
    selection.  We train on the photometry.  You can see the selection in
    \autoref{fig:mock_data_photometric_background_selection}.  You can see both
    the on-stream and off-stream labels, blue and black respectively.  We select
    using an astrometric selection. In the photometry you can see that the
    on-stream selection has two populations, drawn from the isochrone and drawn
    from the background The off-stream selection, meanwhile, has only the
    background population. Next we train the full model.
